Central Limit Theorems for Super Ornstein-Uhlenbeck Processes with stable Branching

### 2019-01-31 supCLT.tex
supCLT.tex: 1101

We want to prove the following Lemma
\begin{lem}\label{lemma2_13}
Let $f:[0,\infty)\rightarrow[1,\infty)$ be a function such that $f\leq e^{\alpha t}$ and $\lim_{t\rightarrow \infty}f(t)=\infty$ Then for any $\mu\in \mathcal M(\mathbb R^d)$ with compact support, there exist $C_4>0$ such that there is
\begin{align}
    \mathbb{\tilde{P}}_{\mu}(\|X_t\|\leq \|\mu\|f(t))\leq C_4 \exp(\beta(\ln f(t)-\alpha t)), \quad t\geq 0.
\end{align}
\end{lem}
\begin{proof}
 Without loss of generality, we assume that $\|\mu\|=1$, By Chebyshev's Inequality and formula \eqref{laplaceexpress}, we get
\begin{align*}
    \mathbb{\tilde{P}}_{\mu}[\|X_t\|\leq f(t)]&=\mathbb{\tilde{P}}_{\mu}[e^{-\lambda\|X_t\|}\geq e^{-\lambda f(t)}]\leq e^{\lambda f(t)}\mathbb{\tilde{P}}_{\mu}[e^{-\lambda \|X_t\|)}]\\
    &\leq \frac{\|\mu\|}{1-e^{-\|\mu\|\alpha^*}}e^{\lambda f(t)}\left|v_t(\lambda)-v_t(\lambda+\alpha^*)\right|
\end{align*}
Let $w_t(\lambda)=\alpha \lambda^{-\beta}e^{-\alpha \beta t}+1-e^{-\alpha\beta t},~ t\geq 0,\lambda\geq0$, $v_t(\lambda)=\alpha^{1/\beta}w_t(\lambda)^{-1/\beta}$.
\begin{align*}
    \left|v_t(\lambda)-v_t(\lambda+\alpha^*)\right|&\leq\frac {\alpha^{1/\beta}}{\beta}\sup_{s\in [\lambda,\lambda+\alpha^*]}w_t(s)^{-1/\beta-1}\cdot\left|w_t(\lambda)-w_t(\lambda+\alpha^*)\right|\\
    &\leq  \frac{\alpha^{1/\beta+1}}{\beta}\sup_{s\in [\lambda,\lambda+\alpha^*]}w_t(s)^{-1/\beta-1}\left|\frac{1}{\lambda^{\beta}}-\frac{1}{(\lambda+\alpha^*)^{\beta}}\right|e^{-\alpha\beta t}\\
    &\leq  \frac{\alpha^{1/\beta+1}}{\beta}\sup_{s\in [\lambda,\lambda+\alpha^*]}w_t(s)^{-1/\beta-1}\frac{2}{\lambda^{\beta}}e^{-\alpha\beta t}
\end{align*}
Therefore,
\begin{align*}
    \mathbb{\tilde{P}}_{\mu}[\|X_t\|\leq f(t)]\leq \frac{\alpha^{1/\beta+1}}{\beta}\sup_{s\in [\lambda,\lambda+\alpha^*]}w_t(s)^{-1/\beta-1}\frac{2}{\lambda^{\beta}}e^{-\alpha\beta t}\cdot \frac{1}{1-e^{-\alpha^*}} e^{\lambda f(t)}.
\end{align*}
Take $\lambda=\frac{1}{f(t)}$ into the above inequality, we have
\begin{align*}
    \mathbb{\tilde{P}}_{\mu}[\|X_t\|\leq f(t)]\leq \frac{2 e \alpha^{1+1/\beta}}{\beta (1-e^{-\alpha^*})}\cdot\sup_{s\in [1/f(t),1/f(t)+\alpha^*]}w_t(s)^{-1/\beta-1}\exp(\beta(\ln f(t)-\alpha t))
\end{align*}
Notice that
\begin{align*}
    w_t(s)^{-1/\beta-1}&\leq \frac{1}{(\alpha s^{-\beta}e^{-\alpha \beta t})^{1/
    \beta+1}}\mathbf{1}_{\{t\leq 1\}}+\frac{1}{(1-e^{-\alpha\beta t})^{1/\beta+1}}\mathbf{1}_{t\geq 1}\\
    &\leq \frac{s^{1+\beta}e^{\alpha(1+\beta)t}}{\alpha^{1/\beta +1}}\mathbf{1}_{\{t\leq 1\}}+\frac{1}{(1-e^{-\alpha\beta })^{1/\beta+1}}.
\end{align*}
This is to say
\begin{align*}
    \sup_{s\in [1/f(t),1/f(t)+\alpha^*]}w_t(s)^{-1/\beta-1}&\leq\sup_{s\in [1/f(t),1/f(t)+\alpha^*]}\frac{s^{1+\beta}e^{\alpha(1+\beta)t}}{\alpha^{1/\beta +1}}\mathbf{1}_{\{t\leq 1\}}+\frac{1}{(1-e^{-\alpha\beta })^{1/\beta+1}}\\
    &\leq \frac{(1+\alpha^*)^{1+\beta}e^{\alpha(1+\beta)}}{\alpha^{1/\beta+1}}+\frac{1}{(1-e^{-\alpha\beta })^{1/\beta+1}}
\end{align*}
We conclude the lemma by taking $C_4= \frac{2 e \alpha^{1+1/\beta}}{\beta (1-e^{-\alpha^*})}\left(\frac{(1+\alpha^*)^{1+\beta}e^{\alpha(1+\beta)}}{\alpha^{1/\beta+1}}+\frac{1}{(1-e^{-\alpha\beta })^{1/\beta+1}}\right)$.
\end{proof}
\begin{lem}\label{lemma28}
  For any $\epsilon>0$, let $\mathcal{A}_t(\epsilon):=\left\{ \|X_t\|\in \|\mu\|\left(e^{(\alpha-\epsilon)t},e^{(\alpha+\epsilon)t}\right)\right\}$, there exists $C_5>0$ and $\delta_1>0$ such that
  $$\mathbb{\tilde{P}}_{\mu}\left(\mathcal{A}_t(\epsilon)^c\right)\leq C_5 e^{-\delta_1 t},\quad t\geq 0.$$
\end{lem}

\begin{proof}
    First, for any $\epsilon>0$, using Markov inequality, we get
    $$\mathbb{\tilde{P}}_{\mu}(\|X_t\|\geq\|\mu\|e^{(\alpha+\epsilon)t})\leq\frac{\mathbb{\tilde{P}}_{\mu}[\|X_t\|]}{\|\mu\|e^{(\alpha+\epsilon)t}}\leq e^{-\epsilon t}.$$
    For another side, using Lemma \ref{lemma2_13}, we have
    $$\mathbb{P}_{\mu}\left(\|X_t\|\leq \|\mu\|e^{(\alpha-\epsilon)t}|D^c\right)\leq C_4 e^{-\beta\epsilon t}, $$
Therefore,
\begin{align*}
    \mathbb{P}_{\mu}\left(\mathcal{A}_t(\epsilon)^c|D^c\right)\leq \mathbb{P}_{\mu}(\|X_t\|\geq\|\mu\|e^{(\alpha+\epsilon)t}|D^c)+\mathbb{P}_{\mu}\left(\|X_t\|\leq \|\mu\|e^{(\alpha-\epsilon)t}|D^c\right)\leq(C_4+1)e^{-\beta \epsilon t }
\end{align*}
\end{proof}

%\subsection{Parameter $m_k[g]$}
{\bf (Jianjie: Can I add the condition $t\in \mathbb{N}$ above this subsection and omit the case $t \notin \mathbb{N}$.)}
\subsection{Parameters}
 In this subsection, we will introduce an important parameter $m_k[f],~f\in\mathcal{P}$, which is a parameter of $(1+\beta)$-stable distribution. Let $Z_f(x)=Z_f(1,x)$, thus
 $$Z_f(x)=\int_0^1 T^{\alpha}_{1-s}(-iT_s^{\alpha}f)^{1+\beta}(x)~ds,$$
 Let
 \begin{align}
      m_k[f]:=e^{-\alpha(k+1)}\langle Z_{f_k},\varphi\rangle.
 \end{align}
\begin{lem}\label{mgineq1}
Let $f\in\mathcal{P}$, there exists constant $C_6>0$ such that for any $k\in \{0,1,...,t\}$, we have
$$|m_k[f]|\leq C_6 e^{(\alpha\beta-\kappa(f)b(1+\beta))k}.$$
\end{lem}
\begin{proof}
Let $R_0$ be the control function in \eqref{eq:semigroupineq}, as $f$ satisfies \eqref{eq:gcontrol1} by $C_f=1, \kappa=\kappa(f)$ and $R_0^f=R_0$, by \eqref{eq: zineq2}, there exists $R_2^f\in \mathcal{P}$ such that
\begin{align}
    |Z_{f_k}(x)|\leq e^{(\alpha-\kappa(f)b)(1+\beta)k}R_2^f(x), \quad x\in \mathbb{R}^d, k\in\mathbb{N}.
\end{align}
This implies the result by simply calculating.
\end{proof}

@@

{\bf In Milos' paper, he says $e^{\theta^{1+\beta}e^{\alpha}m_k[f]}$ is a characteristic function, but no explanation.}
\begin{lem}
For any $x,y\in \mathbb{C}$, $|e^x-e^y|\leq (e^{Re(x)}\vee e^{Re(y)})|x-y|$.
\begin{proof}
let $z=Re(y)+Im(x)$,
\begin{align}\label{estim}
    |e^x-e^y|\leq|e^x-e^z|+|e^z-e^y|\leq |e^{Re(x)}-e^{Re(y)}|+e^{Re(y)}|x-y|\leq (e^{Re(x)}\vee e^{Re(y)})|x-y|.
\end{align}
\end{proof}
\end{lem}
\begin{lem}\label{lemma31}

 Let $f\in \mathcal{P}$, assume that $\alpha\beta\leq \kappa(f)b(1+\beta)$, then for any  $k\in\mathbb{N}$ and $\mu \in \mathcal{M}(R^d)$ with compact support, under $\mathbb{P}_{\mu}(\cdot | D ^c)$, we have
 \begin{align}
      \frac{M_k^t[f]}{F_k(X_{t-k-1})}\xrightarrow{d}\zeta_k, \quad t\rightarrow \infty, \label{limitdistribution1}
 \end{align}
 where $\zeta_k$ is a $(1+\beta)$-stable random variable with characteristic function
 $$\mathbb{E}e^{i\theta\zeta_k}=\exp\left[\theta^{1+\beta}e^{\alpha}m_k[f]\right].$$
 \end{lem}
     Let $v_{f_k}(x,\theta)=v_{f_k}(1,x,\theta),\tilde{v}_{f_k}(x,\theta)=\tilde{v}_{f_k}(1,x,\theta)$ and $\tilde{\theta}_{t,k}=\frac{\theta}{F_k(X_{t-k-1})}$. For any $k\in\mathbb{N}$ and $t>k$, we have
        &\mathbb{P}_{\mu}[\exp(i\theta\frac {M_k^t[f]}{F_k(X_{t-k-1})})]\\
        &=\mathbb{P}_{\mu}\left[\mathbb{\tilde{P}}_{\mu}[\exp(i\theta\frac{M_k^t[f]}{F_k(X_{t-k-1})})|\mathcal{F}_{t-k-1}]\right]\\
        &=\mathbb{P}_{\mu}\left[\exp\left(\langle v_{f_k}(\cdot,\tilde{\theta}_{t,k}),X_{t-k-1}\rangle-i\tilde{\theta}_{t,k}\langle T_{k+1}^{\alpha}f, X_{t-k-1}\rangle\right)\right].\\
        \label{condition mean}
        &=\mathbb{P}_{\mu}\left[\exp(\langle v_{f_k}(\cdot,\tilde{\theta}_{t,k})-\tilde{v}_{f_k}(\cdot, \tilde{\theta}_{t,k}),X_{t-k-1}\rangle+\langle Z_{f_k}(\cdot,\tilde{\theta}_{t,k}),X_{t-k-1}\rangle)\right]\\
       To get the conclusion of Lemma \ref{lemma31}, it suffices to show that
           \mathbb{P}_{\mu}\left(\exp(i\theta\frac{M_k^t[f]}{F_k(X_{t-k-1}}))\mathbf{1}_{D^c}\right)\xrightarrow{t\rightarrow \infty}\mathbb{P}_{\mu}(D^c)\exp(\theta^{1+\beta}e^{\alpha}m_k[f]).
       Fix $\gamma_0\in (0,\beta)$, let $p=\min\{b,\frac{\alpha\gamma_0}{2(1+\gamma_0)}\}$ and Let $\epsilon_0=\min\{\frac{\alpha\beta}{2(1+2\beta)},\frac{p}{2}\}$.
        Recall that $\mathcal{A}_t(\epsilon_0)=\{\|X_t\|\in\|\mu\|(e^{(\alpha-\epsilon_0)t},e^{(\alpha+\epsilon_0)t})\}$.
        &\left|\mathbb{P}_{\mu}\left[\left(\exp(i\theta\frac{M_k^t[f]}{F_k(X_{t-k-1}})-\exp(\theta^{1+\beta}e^{\alpha}m_k[f])\right)\mathbf{1}_{D^c}\right]\right| \\
        &\leq\left|\mathbb{P}_{\mu}\left[\left(\exp(i\theta\frac{M_k^t[f]}{F_k(X_{t-k-1}})-\exp(\theta^{1+\beta}e^{\alpha}m_k[f])\right)\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\right]\right|\\
        &+\left|\mathbb{P}_{\mu}\left[\left(\exp(i\theta\frac{M_k^t[f]}{F_k(X_{t-k-1}})-\exp(\theta^{1+\beta}e^{\alpha}m_k[f])\right)\mathbf{1}_{D^c  \cap\mathcal{A}^c_{t-k-1}(\epsilon_0)}\right]\right|
         Let $c=|\theta^{1+\beta}e^{\alpha}m_k[f]|$. By lemma \ref{lemm28}, there exists $\delta_1>0$ and $C_5>0$ such that
            &\left|\mathbb{P}_{\mu}\left[\left(\exp(i\theta\frac{M_k^t[f]}{F_k(X_{t-k-1}})-\exp(\theta^{1+\beta}e^{\alpha}m_k[f])\right)\mathbf{1}_{D^c  \cap\mathcal{A}^c_{t-k-1}(\epsilon_0)}\right]\right| \\
            &\leq \mathbb{P}_{\mu}(D^c)\mathbb{\tilde{P}}_{\mu}(\mathcal{A}_{t-k-1})\leq (1+e^c)C_5\mathbb{P}_{\mu}(D^c)e^{-\delta_1(t-k-1)}.
       On the other hand, by formula \eqref{condition mean} and Lemma \ref{estim}
        &\left|\mathbb{P}_{\mu}\left([\exp(i\theta \frac {M_k^t[f]}{F_k(X_{t-k-1})})]-\exp(\theta^{1+\beta}e^{\alpha}m_k[f])\right)\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\right|\\
        &\leq e^c\mathbb{P}_{\mu}\left[\left|\langle v_{f_k}(\cdot,\tilde{\theta}_{t,k})-\tilde{v}_{f_k}(\cdot,\tilde{\theta}_{t,k}), X_{t-k-1}\rangle\right|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\right]\\
        \label{ineqinlem31}
        &+e^c\mathbb{P}_{\mu}\left[\left|\langle Z_{f_k}(\cdot,\tilde{\theta}_{t,k}),X_{t-k-1}\rangle-\theta^{1+\beta}e^{\alpha}m_k[f]\right|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\right].
Step 1.  We will show that for each $\mu \in\mathcal{M}(\mathbb{R}^d)$ with compact support, there exists $C_6>0$, such that for any $\theta\in \mathbb{R}$, $k\in\mathbb{N}$ and $t>k$,
    \label{lemma31q}
        \mathbb{P}_{\mu}\left[\left|\langle v_{f_k}(\cdot,\tilde{\theta}_{t,k})-\tilde{v}_{f_k}(\cdot,\tilde{\theta}_{t,k}), X_{t-k-1}\rangle\right|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\right]\leq C_6|\theta|^{1+2\beta}e^{-\frac{\alpha\beta}{2(1+\beta)}(t-k-1)}.
Combining with \eqref{eq:semigroupineq}, \eqref{eq:gcontrol1} and Lemma \ref{lemma2}, there exist $R_1^f,R_6>0$ such that
    & |v_{f_k}(x,\tilde{\theta}_{t,k})-\tilde{v}_{f_k}(x,\tilde{\theta}_{t,k})|\leq |\tilde{\theta}_{t,k} e^{(\alpha-\kappa(f) b)k}|^{1+2\beta}R^f_1(x),\\
    & |T_t (R^f_1)(x)|\leq R_6(x), \quad x\in \mathbb{R}^d,t\geq 0, \theta \in \mathbb{R}.
%Let $R_1$ be the control function in Lemma \ref{lemma2}. According to \eqref{eq:semigroupineq}, there exists $R_6\in \mathcal{P}$, satisfying $|T_t %(R_1)(x)|\leq R_6(x)$, for each $t>0$ and $x\in \mathbb{R}^d$.

For any $\theta\in \mathbb{R}$, $k\in \mathbb{N}$ and $t>k$, on the event $\mathcal{A}_{t-k-1}$, we have

>>>>

We want to prove the following Lemma
\begin{lem}\label{lemma2_13}
Let $f:[0,\infty)\rightarrow[1,\infty)$ be a function such that $f\leq e^{\alpha t}$ and $\lim_{t\rightarrow \infty}f(t)=\infty$ Then for any $\mu\in \mathcal M(\mathbb R^d)$ with compact support, there exist $C_4>0$ such that there is
\begin{align}
    \mathbb{\tilde{P}}_{\mu}(\|X_t\|\leq \|\mu\|f(t))\leq C_4 \exp(\beta(\ln f(t)-\alpha t)), \quad t\geq 0.
\end{align}
\end{lem}
\begin{proof}
 Without loss of generality, we assume that $\|\mu\|=1$, By Chebyshev's Inequality and formula \eqref{laplaceexpress}, we get
\begin{align*}
    \mathbb{\tilde{P}}_{\mu}[\|X_t\|\leq f(t)]&=\mathbb{\tilde{P}}_{\mu}[e^{-\lambda\|X_t\|}\geq e^{-\lambda f(t)}]\leq e^{\lambda f(t)}\mathbb{\tilde{P}}_{\mu}[e^{-\lambda \|X_t\|)}]\\
    &\leq \frac{\|\mu\|}{1-e^{-\|\mu\|\alpha^*}}e^{\lambda f(t)}\left|v_t(\lambda)-v_t(\lambda+\alpha^*)\right|
\end{align*}
Let $w_t(\lambda)=\alpha \lambda^{-\beta}e^{-\alpha \beta t}+1-e^{-\alpha\beta t},~ t\geq 0,\lambda\geq0$, $v_t(\lambda)=\alpha^{1/\beta}w_t(\lambda)^{-1/\beta}$.
\begin{align*}
    \left|v_t(\lambda)-v_t(\lambda+\alpha^*)\right|&\leq\frac {\alpha^{1/\beta}}{\beta}\sup_{s\in [\lambda,\lambda+\alpha^*]}w_t(s)^{-1/\beta-1}\cdot\left|w_t(\lambda)-w_t(\lambda+\alpha^*)\right|\\
    &\leq  \frac{\alpha^{1/\beta+1}}{\beta}\sup_{s\in [\lambda,\lambda+\alpha^*]}w_t(s)^{-1/\beta-1}\left|\frac{1}{\lambda^{\beta}}-\frac{1}{(\lambda+\alpha^*)^{\beta}}\right|e^{-\alpha\beta t}\\
    &\leq  \frac{\alpha^{1/\beta+1}}{\beta}\sup_{s\in [\lambda,\lambda+\alpha^*]}w_t(s)^{-1/\beta-1}\frac{2}{\lambda^{\beta}}e^{-\alpha\beta t}
\end{align*}
Therefore,
\begin{align*}
    \mathbb{\tilde{P}}_{\mu}[\|X_t\|\leq f(t)]\leq \frac{\alpha^{1/\beta+1}}{\beta}\sup_{s\in [\lambda,\lambda+\alpha^*]}w_t(s)^{-1/\beta-1}\frac{2}{\lambda^{\beta}}e^{-\alpha\beta t}\cdot \frac{1}{1-e^{-\alpha^*}} e^{\lambda f(t)}.
\end{align*}
Take $\lambda=\frac{1}{f(t)}$ into the above inequality, we have
\begin{align*}
    \mathbb{\tilde{P}}_{\mu}[\|X_t\|\leq f(t)]\leq \frac{2 e \alpha^{1+1/\beta}}{\beta (1-e^{-\alpha^*})}\cdot\sup_{s\in [1/f(t),1/f(t)+\alpha^*]}w_t(s)^{-1/\beta-1}\exp(\beta(\ln f(t)-\alpha t))
\end{align*}
Notice that
\begin{align*}
    w_t(s)^{-1/\beta-1}&\leq \frac{1}{(\alpha s^{-\beta}e^{-\alpha \beta t})^{1/
    \beta+1}}\mathbf{1}_{\{t\leq 1\}}+\frac{1}{(1-e^{-\alpha\beta t})^{1/\beta+1}}\mathbf{1}_{t\geq 1}\\
    &\leq \frac{s^{1+\beta}e^{\alpha(1+\beta)t}}{\alpha^{1/\beta +1}}\mathbf{1}_{\{t\leq 1\}}+\frac{1}{(1-e^{-\alpha\beta })^{1/\beta+1}}.
\end{align*}
This is to say
\begin{align*}
    \sup_{s\in [1/f(t),1/f(t)+\alpha^*]}w_t(s)^{-1/\beta-1}&\leq\sup_{s\in [1/f(t),1/f(t)+\alpha^*]}\frac{s^{1+\beta}e^{\alpha(1+\beta)t}}{\alpha^{1/\beta +1}}\mathbf{1}_{\{t\leq 1\}}+\frac{1}{(1-e^{-\alpha\beta })^{1/\beta+1}}\\
    &\leq \frac{(1+\alpha^*)^{1+\beta}e^{\alpha(1+\beta)}}{\alpha^{1/\beta+1}}+\frac{1}{(1-e^{-\alpha\beta })^{1/\beta+1}}
\end{align*}
We conclude the lemma by taking $C_4= \frac{2 e \alpha^{1+1/\beta}}{\beta (1-e^{-\alpha^*})}\left(\frac{(1+\alpha^*)^{1+\beta}e^{\alpha(1+\beta)}}{\alpha^{1/\beta+1}}+\frac{1}{(1-e^{-\alpha\beta })^{1/\beta+1}}\right)$.
\end{proof}
Define $\mathcal{A}_t(\epsilon):=\left\{ \|X_t\|\in \|\mu\|\left(e^{(\alpha-\epsilon)t},e^{(\alpha+\epsilon)t}\right)\right\},\quad \epsilon,t>0$.
\begin{lem}\label{lemma28}
  For any $\epsilon>0$, $t>0$ and $\mu \in \mathcal{M}(\mathbb{R}^d)$ with compact support, there exists $C_5>0$ and $\delta_1>0$ such that
  $$\mathbb{\tilde{P}}_{\mu}\left(\mathcal{A}_t(\epsilon)^c\right)\leq C_5 e^{-\delta_1 t}.$$
\end{lem}

\begin{proof}
    First, for any $\epsilon>0$, using Markov inequality, we get
    $$\mathbb{\tilde{P}}_{\mu}(\|X_t\|\geq\|\mu\|e^{(\alpha+\epsilon)t})\leq\frac{\mathbb{\tilde{P}}_{\mu}[\|X_t\|]}{\|\mu\|e^{(\alpha+\epsilon)t}}\leq \frac{1}{\mathbb{P}_{\mu}(D^c)}e^{-\epsilon t}.$$
    For another side, using Lemma \ref{lemma2_13}, we have
    $$\mathbb{\tilde{P}}_{\mu}\left(\|X_t\|\leq \|\mu\|e^{(\alpha-\epsilon)t}\right)\leq C_4 e^{-\beta\epsilon t}, $$
Therefore,
\begin{align*}
    \mathbb{\tilde{P}}_{\mu}\left(\mathcal{A}_t(\epsilon)^c\right)\leq \mathbb{\tilde{P}}_{\mu}(\|X_t\|\geq\|\mu\|e^{(\alpha+\epsilon)t})+\mathbb{P}_{\mu}\left(\|X_t\|\leq \|\mu\|e^{(\alpha-\epsilon)t}\right)\leq(C_4+\frac{1}{\mathbb{P}_{\mu}(D^c)})e^{-\beta \epsilon t }
\end{align*}
\end{proof}

%\subsection{Parameter $m_k[g]$}
{\bf (Jianjie: Can I add the condition $t\in \mathbb{N}$ above this subsection and omit the case $t \notin \mathbb{N}$.)}
\subsection{Parameters}
 In this subsection, we will introduce an important parameter $m_k[f],~f\in\mathcal{P}$, which is a parameter of $(1+\beta)$-stable distribution. Let $Z_f(x)=Z_f(1,x)$, thus
 $$Z_f(x)=\int_0^1 T^{\alpha}_{1-s}(-iT_s^{\alpha}f)^{1+\beta}(x)~ds,$$
 Let
 \begin{align}\label{parameter_mk}
      m_k[f]:=e^{-\alpha(k+1)}\langle Z_{f_k},\varphi\rangle.
 \end{align}
\begin{lem}\label{mgineq1}
Let $f\in\mathcal{P}$, there exists constant $C_6>0$ such that for any $k\in \{0,1,...,t\}$, we have
$$|m_k[f]|\leq C_6 e^{(\alpha\beta-\kappa(f)b(1+\beta))k}.$$
\end{lem}
\begin{proof}
Let $R_0$ be the control function in \eqref{eq:semigroupineq}, as $f$ satisfies \eqref{eq:gcontrol1} by $C_f=1, \kappa=\kappa(f)$ and $R_0^f=R_0$, by \eqref{eq: zineq2}, there exists $R_2^f\in \mathcal{P}$ such that
\begin{align}
    |Z_{f_k}(x)|\leq e^{(\alpha-\kappa(f)b)(1+\beta)k}R_2^f(x), \quad x\in \mathbb{R}^d, k\in\mathbb{N}.
\end{align}
This implies the result by simply calculating.
\end{proof}

@@

{\bf In Milos' paper, he says $e^{\theta^{1+\beta}e^{\alpha}m_k[f]}$ is a characteristic function, but no explanation.}
\begin{lem}\label{lemma31}
For any $x,y\in \mathbb{C}$, $|e^x-e^y|\leq (e^{Re(x)}\vee e^{Re(y)})|x-y|$.
\end{lem}
\begin{proof}
let $z=Re(y)+iIm(x)$,
\begin{align}\label{estim}
    |e^x-e^y|\leq|e^x-e^z|+|e^z-e^y|\leq |e^{Re(x)}-e^{Re(y)}|+e^{Re(y)}|x-y|\leq (e^{Re(x)}\vee e^{Re(y)})|x-y|.
\end{align}
\end{proof}
\begin{lem}\label{lemma32}
Recall $\mathcal{A}_t(\epsilon)=\{\|X_t\|\in\|\mu\|(e^{(\alpha-\epsilon_0)t},e^{(\alpha+\epsilon_0)t})\},~\epsilon,t>0$, then for any $t>0$, we have
\begin{align}
    \lim_{t\rightarrow\infty}\mathcal{A}_t(\epsilon)=D^c
\end{align}
\end{lem}
\begin{proof}
    We just need to prove 
    \begin{align}
        D^c \subset \liminf_{t\rightarrow\infty}\mathcal{A}_t(\epsilon)\subset \limsup_{t\rightarrow\infty}\mathcal{A}_t(\epsilon)\subset D^c.
    \end{align}
    for any $\omega\in D$, there exists $S>0$, such that $\|X_t(\omega)\|=0,~t\geq T$. Thus $\omega \notin \cup_{t\geq S}\mathcal{A}_t(\epsilon)$ and $\omega\notin  \limsup_{t\rightarrow\infty}\mathcal{A}_t(\epsilon):=\cap_{S\geq 0}\cup_{t\geq S}\mathcal{A}_t(\epsilon)$ imply that $\limsup_{t\rightarrow\infty}\mathcal{A}_t(\epsilon)\subset D^c$.

    For any $\omega \in D^c$, there exists $\delta>0$ such that $W_{\infty}(\omega)\in(\delta,\frac{1}{\delta})$,\deleted{$~\mathbb{P}_{\mu}$-a.s}. As $W_t$ converges to $W_{\infty}$ $\mathbb{P}_{\mu}$-a.s, there exists $S_1>0$ such that for any $t\geq S_1$, we have $\frac{\delta}{2}\leq W_t(\omega)\leq 2\delta,$\deleted{$~\mathbb{P}_{\mu}$-a.s}. Taking $S_2>0$ such that for any $t>S_2$, $\|\mu\|e^{-\epsilon t}<\frac{\delta}{2}$ and $\|\mu\|e^{-\epsilon t}>2\delta$, then $\omega\in \mathcal{A}_t(\epsilon),~t>S:=\max\{S_1,S_2\}$ implies $\omega \in \liminf_{t\rightarrow \infty}\mathcal{A}_t(\epsilon):=\cup_{S>0}\cap_{t\geq S}\mathcal{A}_t(\epsilon)$.
\end{proof}

\begin{lem}
For any $f\in \mathcal{P}$ and $k\in \mathbb{N}$, let $m_k[f]$ be the parameter defined in \eqref{parameter_mk}, then the function $\theta\mapsto \exp(\theta^{1+\beta}e^{\alpha}m_k[f])$ defined on $\theta\in(0,\infty)$ is a characteristic function of some $(1+\beta)$-stable random variable.
\end{lem}
\begin{proof}
    Let $J=\langle\int_0^1 T_{1-s}^{\alpha}(-T^{\alpha}_s f)^{1+\beta}(\cdot)ds,\varphi\rangle$, then 
    \begin{align}
        m_k[f]=J e^{-\alpha(k+1)}\cdot i^{1+\beta}=J e^{-\alpha(k+1)}\cos\frac{(1+\beta)\pi}{2}\big(1+i\tan\frac{(1+\beta)\pi}{2}\big).
    \end{align}
Thus
\begin{align}
    \exp(\theta^{1+\beta}e^{\alpha}m_k[f])=\exp\big(J e^{-\alpha k}\cos\frac{(1+\beta)\pi}{2}\cdot\theta^{1+\beta}\big(1+i\tan\frac{(1+\beta)\pi}{2}\big)\big)
\end{align}
B \cite[Theorem 14.15]{Sato1990Levy}, we get the result.
\end{proof}
{\bf Jianjie: I think the proof has some problem, as we are not sure $J$ is negative or not,}
\begin{lem}\label{lemma33}

 Let $f\in \mathcal{P}$, assume that $\alpha\beta\leq \kappa(f)b(1+\beta)$, then for any  $k\in\mathbb{N}$ and $\mu \in \mathcal{M}(\mathbb{R}^d)$ with compact support, under $\mathbb{P}_{\mu}(\cdot | D ^c)$, we have
 \begin{align}
      \frac{M_k^t[f]}{F_k(X_{t-k-1})}\xrightarrow{d}\zeta_k, \quad t\rightarrow \infty, \label{limitdistribution1}
 \end{align}
 where $\zeta_k$ is a $(1+\beta)$-stable random variable with characteristic function
 $$\mathbb{E}e^{i\theta\zeta_k}=\exp\left[\theta^{1+\beta}e^{\alpha}m_k[f]\right].$$
 \end{lem}

 \begin{proof}
     Let $v_{f_k}(x,\theta)=v_{f_k}(1,x,\theta),\tilde{v}_{f_k}(x,\theta)=\tilde{v}_{f_k}(1,x,\theta)$ and $\tilde{\theta}_{t,k}=\frac{\theta}{F_k(X_{t-k-1})}$. For any $k\in\mathbb{N}$ and $t>k$, we have
         \begin{align}
        &\mathbb{P}_{\mu}\big[\exp(i\theta\frac {M_k^t[f]}{F_k(X_{t-k-1})})\big|\mathcal{F}_{t-k-1}\big]\\
        &=\exp\big(\langle v_{f_k}(\cdot,\tilde{\theta}_{t,k}),X_{t-k-1}\rangle-i\tilde{\theta}_{t,k}\langle T_{k+1}^{\alpha}f, X_{t-k-1}\rangle\big).\\
        \label{condition mean}
        &=\exp\big(\langle v_{f_k}(\cdot,\tilde{\theta}_{t,k})-\tilde{v}_{f_k}(\cdot, \tilde{\theta}_{t,k}),X_{t-k-1}\rangle+\langle Z_{f_k}(\cdot,\tilde{\theta}_{t,k}),X_{t-k-1}\rangle\big)\\
       \end{align}
         Fix $\gamma_0\in (0,\beta)$, let $p=\min\{b,\frac{\alpha\gamma_0}{2(1+\gamma_0)}\}$ and $\epsilon_0=\min\{\frac{\alpha\beta}{2(1+2\beta)},\frac{p}{2}\}$.
       To get the conclusion of Lemma \ref{lemma33}, it suffices to show that
       \begin{align}
           \mathbb{P}_{\mu}\Big(\exp(i\theta\frac{M_k^t[f]}{F_k(X_{t-k-1}}))\mathbf{1}_{D^c}\Big)\xrightarrow{t\rightarrow \infty}\mathbb{P}_{\mu}(D^c)\exp(\theta^{1+\beta}e^{\alpha}m_k[f]).
       \end{align}
\deleted{
        \begin{align}
        &\left|\mathbb{P}_{\mu}\left[\left(\exp(i\theta\frac{M_k^t[f]}{F_k(X_{t-k-1}})-\exp(\theta^{1+\beta}e^{\alpha}m_k[f])\right)\mathbf{1}_{D^c}\right]\right| \\
        &\leq\left|\mathbb{P}_{\mu}\left[\left(\exp(i\theta\frac{M_k^t[f]}{F_k(X_{t-k-1}})-\exp(\theta^{1+\beta}e^{\alpha}m_k[f])\right)\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\right]\right|\\
        &+\left|\mathbb{P}_{\mu}\left[\left(\exp(i\theta\frac{M_k^t[f]}{F_k(X_{t-k-1}})-\exp(\theta^{1+\beta}e^{\alpha}m_k[f])\right)\mathbf{1}_{D^c  \cap\mathcal{A}^c_{t-k-1}(\epsilon_0)}\right]\right|
        \end{align}
         Let $c=|\theta^{1+\beta}e^{\alpha}m_k[f]|$. By lemma \ref{lemm28}, there exists $\delta_1>0$ and $C_5>0$ such that
       \begin{align}
            &\left|\mathbb{P}_{\mu}\left[\left(\exp(i\theta\frac{M_k^t[f]}{F_k(X_{t-k-1}})-\exp(\theta^{1+\beta}e^{\alpha}m_k[f])\right)\mathbf{1}_{D^c  \cap\mathcal{A}^c_{t-k-1}(\epsilon_0)}\right]\right| \\
            &\leq \mathbb{P}_{\mu}(D^c)\mathbb{\tilde{P}}_{\mu}(\mathcal{A}_{t-k-1})\leq (1+e^c)C_5\mathbb{P}_{\mu}(D^c)e^{-\delta_1(t-k-1)}.
       \end{align}
       }
     Equivalently, by Lemma \ref{lemma32}， we just need to prove
     \begin{align}
        \Big|\mathbb{P}_{\mu}\Big[\big(\exp(i\theta \frac {M_k^t[f]}{F_k(X_{t-k-1})})-\exp(\theta^{1+\beta}e^{\alpha}m_k[f])\big)\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\Big]\Big|\xrightarrow{t\rightarrow\infty} 0.
    \end{align}
